Solving a probabilistic planning problem by presenting a history in the field of probabilistic planning

### 2014-04-13 FinalPaper/paper.tex
changed domains, veel meer op het doel van de paper richten, alles echt uitleggen, waarom wel of niet probabilistic interesting etc

\author{I.C.T.M Speek, A.C. Stolwijk}

@@

\todo{Arian: Still have to add why this problem is valid, or interesting}

Section \ref{sec:domaind} introduces the details of proposed domain. Section \ref{sec:background} introduced the appropriate prior knowledge and Section \ref{sec:domains} and \ref{sec:planners} the interesting domains and planners respectively. Section \ref{sec:experiment} briefly elaborates on a possible experiment set-up and finally Section \ref{sec:conclusion} concludes on the evaluation of the domain and an appropriate planner.

@@

\subsubsection{Goal-oriented MDPs. } Classical goal-oriented problems are specified using the Probabilistic Planning Domain Description Language (PPDDL). PPDDL specifies a probabilistic planning problem as a set of probabilistic actions and an initial and goal state description \cite{FFReplan}. These MDPs are of the form $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in the current state $\mathit{s}$. $\mathit{Pr}$ represents the probability of a state transition $\mathit{(s, a, s')}$ for action $\mathit{a}$ and $\mathit{R(s, a, s')}$ is the reward of applying $\mathit{a}$ to $\mathit{s}$ and generating $\mathit{s'}$ The planning problem is defined as a triple $\mathit{P = (M, s\textsubscript{0}, G}$ where $\mathit{M = (S, A, app, Pr, R)}$ is an MDP, $\mathit{s\textsubscript{0} \in S}$ is the initial state and $\mathit{G \subseteq S}$ is the set of goal states.

@@

To identify unique properties of the domain and identify properties of the
domain that work particularly well for a certain type of planner, we describe
other domains used in the IPPC and compare that with the UAV domain.

\paragraph{Blocksworld:}
A simple domain used in the competition of 2004 is the well known blocksworld
domain. The uncertainty lies in that the gripper, used to move blocks, has a
probability that it drops the blocks to the table. Another difference is that
the blocks are colored, and the goal is to build a tower of certain colored
blocks, rather than a tower with specific blocks. If for example there are
four blue blocks, and the goal is a tower of three blue blocks, it does not
matter which blue blocks are used.

\paragraph{Navigation:}
The navigation domain represents a grid in which a robot must reach a goal.
Every cell offers the robot a different chance of disappearing. The robot needs
to choose a path which gets it to the goal most reliably within the finite
horizon time \cite{sanner2011navigation}.

\paragraph{Traffic:}
This domain represents a simple binary version of the cell transition model
(CTM) for modelling traffic based on the original CTM Tech Report
\cite{sanner2011traffic}. Because of the binary variables and no intermediate
variable restrictions, this model is simplified and ignores traffic aspects
such as turns and turn probabilities. This model also uses concurrent actions
and the total actions has an upper bound of $2^{\#~of~intersections}$.

\paragraph{Elevators:}
The elevators domain has evaluated between the competitions of 2006 and
2011, we describe the latest version. In this domain there are a number of
elevators delivering passengers to either the top or bottom floor. Potential
passengers arrive at any floor at a certain rate (depending on which floor).
The elevators can only move in the direction it is indicating, so passengers
know whether to board or not. The goal of the elevators is to transport as many
as possible passengers to their destinations.

\paragraph{SysAdmin:}
The SysAdmin domain describes a network of connected servers. Each server has
a probability that it shuts down, and if is not running, it has a probability
to reboot. The probability that a server shuts down depends on the number of
running connected servers.

\subsection{Domain Evaluation}

The Blocksworld domain is ideal for
replanning~\cite{FFReplan, little2007probvsreplan}. As the blocks fall on the
table, which then can be picked up again, it has no dead ends. This makes it
probabilistically uninteresting. For this domain FF-Repan performs really well.

The newer  domains, Navigation, Traffic, Elevators and SysAdmin are finite-
horizon domains. Navigation, however, is actually a goal oriented domain, if
the goal is reached in the horizon. The method how this is implemented is that
the goal state is defined as an absorbing state, and there is no reward or cost
associated to staying in the goal state, until the horizon is reached.

\textsc{Gourmand} vastly outperformed the UCT-based PROST, the IPPC-11
probabilistic track winner, by far on goal-oriented domains Navigation and
Crossing Traffic \cite{kolobov2012gourmand}. This is because of the dynamic
lookahead feature of \textsc{Gourmand}. PROST however mildly outperforms
\textsc{Gourmand} on the Game of Life, SysAdmin and the Traffic domain as UCT
does not need to perform expensive Bellman Backups on these domains that
include large branching factors.

The domains are constructed such that it will challenge planners to perform
better. This causes that there are issues with the domains when comparing them
with the real world.

In the navigation problem there is a chance that the robot
disappears after entering a cell. The disappearing action is a dead end.
Disappearing here is a metaphor for the robot breaking down, or that it
disappears from the radar with the base station. In many of such cases it's a
big problem, but can be repaired with a high cost. In the navigation domain a
step to another cell has a cost of 1. If instead of a dead end the cost is $n$
(e.g. 5) instead of 1, which represents the cost of repairing the robot, dead
ends are removed. Without dead ends the problem becomes probabilistic
uninteresting, which makes it suitable for replanning planners.

@@

\section{Related Work}

@@

\section{Conclusion}

>>>>

\author{I.C.T.M Speek \& A.C. Stolwijk}

@@

Section \ref{sec:domaind} introduces the details of proposed domain. Section \ref{sec:background} introduced the appropriate prior knowledge and Section \ref{sec:planners} and  \ref{sec:domains} the interesting planners and domains respectively. Section \ref{sec:related} elaborates on different planning solutions and finally Section \ref{sec:conclusion} concludes on the evaluation of the domain and an appropriate planner.

@@

\subsubsection{Goal-oriented MDPs. } Classical goal-oriented problems are specified using the Probabilistic Planning Domain Description Language (PPDDL). PPDDL specifies a probabilistic planning problem as a set of probabilistic actions and an initial and goal state description \cite{FFReplan}. These MDPs are of the form \\ $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in the current state $\mathit{s}$. $\mathit{Pr}$ represents the probability of a state transition $\mathit{(s, a, s')}$ for action $\mathit{a}$ and $\mathit{R(s, a, s')}$ is the reward of applying $\mathit{a}$ to $\mathit{s}$ and generating $\mathit{s'}$ The planning problem is defined as a triple $\mathit{P = (M, s\textsubscript{0}, G}$ where $\mathit{M = (S, A, app, Pr, R)}$ is an MDP, $\mathit{s\textsubscript{0} \in S}$ is the initial state and $\mathit{G \subseteq S}$ is the set of goal states.

@@

To identify unique properties of the domain that work particularly well for a certain type of planner, we describe
other domains in which FF-Replan or Gourmand performed poorly or excellent and compare these with the UAV domain.

A simple domain in which FF-Replan excelled is the \textsc{Blocksworld}
domain. The uncertainty lies in that the gripper used to move blocks has a
probability of dropping the block. The blocks have certain color properties and 
a preferred order in which the blocks should be build. This is the exact point 
in which the UAV domain differs as it does not yet differentiate between messages.

The \textsc{Navigation} domain represents a grid in which a robot must reach a goal similarly to the UAV domain.
Every cell offers the robot a different chance of disappearing. The robot needs
to choose a path which gets it to the goal most reliably within the finite
horizon time \cite{sanner2011navigation}. Although FF-Replan performed poorly in this domain, \textsc{Gourmand} was 
able to perform much better by using the lookahead value $L$.

The \textsc{Traffic} domain represents a simple binary version of the cell transition model
(CTM) for modeling traffic based on the original CTM Tech Report
\cite{sanner2011traffic}. Because of the binary variables and no intermediate
variable restrictions, this model is simplified and ignores traffic aspects
such as turns and turn probabilities. Although it models the CTM correctly, it isn't a strong
representation of the domain in its real-world equivalent where accidents can occur.
This model differentiates itself as it uses and plans for concurrent actions.

In the latest \textsc{Elevators} domain a number of elevators deliver passengers to either the top or bottom floor. Potential
passengers arrive at any floor at a certain rate (depending on which floor).
The elevators can only move in the direction it is indicating, so passengers
know whether to board or not. The goal of the elevators is to transport as many
as possible passengers to their destinations. This domain is one of the first emerging
optimization problems and is therefore inherently different from its previous goal-related version.

In the same way does the \textsc{SysAdmin} domain describe a network of connected servers. Each server has
a probability that it shuts down or reboots whenever it is down. The probability that a server shuts down depends on the number of
running connected servers. This domain is important as it represents the large branching factors introduced by natural dynamics. The introduction
of the \textsc{noop()} operation increases the size exponentially.

\subsection{Domain Evaluation}
\myworries{hier alleen een evalutie geven, niet wederom een uitleg, anders moet je het hierboven uitleggen. Alles wat je zegt, moet een reden hebben, anders kan het weg}

The \textsc{Blocksworld} domain is ideal for
replanning~\cite{FFReplan, little2007probvsreplan} as it has no dead ends. This makes it
probabilistically uninteresting and thus a classical planning problem in disguise, ideally to solve for FF-Replan.

The domains are constructed to challenge planners to perform
better. This creates issues when comparing the domains to their real-world match as can be easily seen 
in the \textsc{Traffic} domain.

Dead-ends in the \textsc{Navigation} domain are represented by the act of disappearing. 
This is a metaphor for the robot breaking down, or that it
disappears from the radar. Although these actions cause troubles in the system, they can be repaired with a high cost. By replacing dead-ends with high cost actions, the problem becomes less probabilistically interesting. 
Although the problem would become suitable for replanners, one could argue that this would only be valid for less critical applications. When applied for
navigating satellites, the failure of the system would be set as such a high cost, it would essentially represent a dead-end.

@@

\section{Related Work}
\label{sec:related}

@@

\section{Conclusion}
\label{sec:conclusion}
